\documentclass[11pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt}
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Hua Shi}}\\
    \vspace{4pt}
    Sarasota, FL \;|\; +1 (941) 225-1558 \;|\; \href{mailto:hshi@c.ringling.edu}{hshi@c.ringling.edu}\\
    \href{https://www.linkedin.com/in/hua-shi-b1738a389/}{linkedin.com/in/hua-shi-b1738a389}
\end{center}

\vspace{6pt}
\noindent\rule{\textwidth}{0.4pt}

\section*{EDUCATION}
\textbf{Ringling College of Art and Design}, Sarasota, FL \hfill \textit{Expected May 2027}\\
Bachelor of Fine Arts in Computer Animation

\section*{EXPERIENCE}
\textbf{Computer Animator}, Ringling College of Art and Design \hfill \textit{Aug 2023 -- Present}
\begin{itemize}
    \item Produced 20-second animation scenes demonstrating physical weight, force, and character emotion.
    \item Designed characters and environments, planned animation shots with thumbnails, and developed lighting schemas.
    \item Modeled, textured, lit, and animated characters and props using end-to-end production workflows.
\end{itemize}

\textbf{Character Designer}, Ringling College of Art and Design \hfill \textit{Sep 2023 -- Present}
\begin{itemize}
    \item Developed character design variations to support worldbuilding and story requirements.
    \item Presented visual pitches, incorporated critique, and iterated concepts under deadline constraints.
\end{itemize}

\textbf{Concept Artist}, Ringling College of Art and Design \hfill \textit{Sep 2024 -- May 2025}
\begin{itemize}
    \item Created a fully original worldbuilding project from concept development through final visual presentation.
\end{itemize}

\textbf{Freelance Artist}, Multiple Clients (Remote) \hfill \textit{2017 -- Present}
\begin{itemize}
    \item Delivered commissioned character designs, sketches, and illustrations for independent clients.
    \item Produced custom fashion and costume designs for existing character properties.
\end{itemize}

\section*{ADDITIONAL EXPERIENCE \& ACTIVITIES}
\begin{itemize}
    \item Personal Tour Guide, China \hfill \textit{Nov 2025 -- Dec 2025}
    \item Member, Photography Club and Table Tennis Club, Ringling College of Art and Design
\end{itemize}

\section*{SKILLS}
\textbf{Software:} Autodesk Maya, Adobe Premiere Pro, Adobe Photoshop, Nuke, 3D Coat, ZBrush\\
\textbf{Languages:} Mandarin (Native), English (Professional Proficiency)

\end{document}
